Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-27 Dissertation/Thesis/tex/multivehicle.tex
added & edited sec. 7.2 (NRL flight tests), added patrol split screen @ 2 min
got rid of '_ss' to figs for SEH multi-vehicle autonomous exploration (not patrol)

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_1min_ss.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_2min_ss.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_3min_ss.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_4min_ss.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_5min_ss.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_6min_ss.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_7min_ss.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_8min_ss.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_9min_ss.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{3D Occupancy Grid Map of SEH Second Floor}
	\label{fig:sim3DMap}
\end{figure}

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$2$ min}% TODO: generate this figure!
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{The 3D occupancy grid map representation of the SEH second floor is shown during patrol. The robots generate these maps while avoiding collisions with each other, the environment, and a non-cooperative human.}
	\label{fig:Sim3DMapPatrol}
\end{figure}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$2$ min}% TODO: generate this figure!
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{The 2D projected map from of the SEH second floor shows degradation while robots patrol the space. The robots evade the non-cooperative human walking in a rectangular pattern, occasionally capturing the temporarily-occupied space and identifying these cells as occupied on the grid.}
	\label{fig:Sim2DMapPatrol}
\end{figure}

>>>>

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_6min.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_8min.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{3D Occupancy Grid Map of SEH Second Floor}
	\label{fig:sim3DMap}
\end{figure}

@@

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={0cm 0cm 35cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{The 3D occupancy grid map representation of the SEH second floor is shown during patrol. The robots generate these maps while avoiding collisions with each other, the environment, and a non-cooperative human.}
	\label{fig:Sim3DMapPatrol}
\end{figure}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_11min.jpg}
        		\caption{$11$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_13min.jpg}
        		\caption{$13$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={35cm 0cm 0cm 0cm}, clip, width=\columnwidth]{Patrol_Split_Screen_15min.jpg}
        		\caption{$15$ min}
    	\end{subfigure}
	}
	\caption{The 2D projected map from of the SEH second floor shows degradation while robots patrol the space. The robots evade the non-cooperative human walking in a rectangular pattern, occasionally capturing the temporarily-occupied space and identifying these cells as occupied on the grid.}
	\label{fig:Sim2DMapPatrol}
\end{figure}
